A novel physical mechanism for the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-12-12 crystal-gel/nature/Supplementary.tex
Update colloid size from knowledge of actual pixel size. Impacts the main text, supplementary, phase diagram and local volume fraction

Our two constraints are (i) to have the final local volume fraction of the 12-neighboured particles in the crystallising sample to be equal to the theoretical equilibrium crystal volume fraction and (ii) to have the theoretical spinodal line to correspond to the gel region boundary. Starting from our initial estimates of $\sigma$ and $R$ we iteratively converge to $R=80$~nm, $\sigma = 2.25\,\mu$m and a crystal (without defects) at $0.723$.

>>>>

Our two constraints are (i) to have the final local volume fraction of the 12-neighboured particles in the crystallising sample to be equal to the theoretical equilibrium crystal volume fraction and (ii) to have the theoretical spinodal line to correspond to the gel region boundary. Starting from our initial estimates of $\sigma$ and $R$ we iteratively converge to $R=80$~nm, $\sigma = 2.21\,\mu$m and a crystal (without defects) at $0.723$.
